R Notebook

### 2017-07-10 doc/RMD/pop-diff.Rmd
update analyses

```{r geno-div2, fig.width = 10, fig.height = 10, comment = NA}
ptab %>%
  arrange(desc(N), desc(MLG)) %>%
  mutate(Ia = case_when(
    !is.finite(.$p.Ia) ~ "-",
    .$p.Ia == 0.001 ~ paste0(round(.$Ia, 2), "*"),
    .$p.Ia <= 0.01 ~  paste0(round(.$Ia, 2), "-"),
    .$p.Ia <= 0.05 ~  paste0(round(.$Ia, 2), "~"),
    TRUE ~ as.character(round(.$Ia, 2))
  )) %>%
  mutate(rbarD = case_when(
    !is.finite(.$p.rD) ~ "-",
    .$p.rD == 0.001 ~ paste0(round(.$rbarD, 2), "*"),
    .$p.rD <= 0.01 ~  paste0(round(.$rbarD, 2), "-"),
    .$p.rD <= 0.05 ~  paste0(round(.$rbarD, 2), "~"),
    TRUE ~ as.character(round(.$rbarD, 2))
  )) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(N = paste(N, MLG, sep = " (") %>% paste0(")") %>% formatC()) %>%
  mutate(eMLG = paste(eMLG, SE, sep = " (") %>%  paste0(")") %>% formatC()) %>%
  rename(`*h*` = Hexp) %>%
  rename(`$E_5$` = E.5) %>%
  rename(`$I_A$` = Ia) %>%
  rename(`$\\lambda$` = lambda) %>%
  rename(`$\\bar{r}_d$` = rbarD) %>%
  select(-File, -MLG, -SE, -p.rD, -p.Ia) %>% 
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 4:5, 1) %>%
  huxtable::set_align(huxtable::everywhere, -1, "right") %>%
  huxtable::set_col_width(c(1.1, 0.9, 1.3, 0.5, 0.5, 1.2, 0.7, 0.6, 0.6, 0.8)) %>%
  huxtable::print_md(max_width = 80)

>>>>

```{r geno-div2, fig.width = 10, fig.height = 10, comment = NA}
ptab %>%
  arrange(desc(N), desc(MLG)) %>%
  mutate(Ia = case_when(
    !is.finite(p.Ia) ~ "-",
    p.Ia == 0.001 ~ paste0(round(Ia, 2), "*"),
    p.Ia <= 0.01  ~ paste0(round(Ia, 2), "-"),
    p.Ia <= 0.05  ~ paste0(round(Ia, 2), "~"),
    TRUE          ~ as.character(round(Ia, 2))
  )) %>%
  mutate(rbarD = case_when(
    !is.finite(p.rD) ~ "-",
    p.rD == 0.001 ~ paste0(round(rbarD, 2), "*"),
    p.rD <= 0.01  ~ paste0(round(rbarD, 2), "-"),
    p.rD <= 0.05  ~ paste0(round(rbarD, 2), "~"),
    TRUE          ~ as.character(round(rbarD, 2))
  )) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(N = paste(N, MLG, sep = " (") %>% paste0(")") %>% formatC()) %>%
  mutate(eMLG = paste(eMLG, SE, sep = " (") %>%  paste0(")") %>% formatC()) %>%
  rename(`*h*` = Hexp) %>%
  rename(`$E_5$` = E.5) %>%
  rename(`$I_A$` = Ia) %>%
  rename(`$\\lambda$` = lambda) %>%
  rename(`$\\bar{r}_d$` = rbarD) %>%
  select(-File, -MLG, -SE, -p.rD, -p.Ia) %>% 
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 4:5, 1) %>%
  huxtable::set_align(huxtable::everywhere, -1, "right") %>%
  huxtable::set_col_width(c(1.1, 0.9, 1.3, 0.5, 0.5, 1.2, 0.7, 0.6, 0.6, 0.8)) %>%
  huxtable::print_md(max_width = 80)

### 2017-07-10 doc/RMD/wmn-differentiation.Rmd
update analyses

```{r dapc, fig.width = 5, fig.height = 5.5}
setPop(bebug) <- ~Host/Region
bebug_dapc <- dapc(bebug, n.pca = 20, n.da = 2)
scatter(bebug_dapc, #clabel = 0,
        legend = TRUE,
        scree.pca = TRUE, 
        scree.da = FALSE,
        # col = viridis::plasma(3), 
        bg.inset = "grey90",
        bg = "grey90")

ggcompoplot::ggcompoplot(bebug_dapc, bebug) + #, pal = viridis::plasma(3)) +
  theme(legend.position = "top")
```

>>>>

```{r dapc, fig.width = 5, fig.height = 4.5}
setPop(bebug) <- ~Host
bebug_dapc <- dapc(bebug, n.pca = 20, n.da = 2)
scatter(bebug_dapc, #clabel = 0,
        legend = TRUE,
        scree.pca = TRUE, 
        scree.da = FALSE,
        col = viridis::plasma(3, end = 0.85),
        bg.inset = "grey90",
        bg = "grey90")

ggcompoplot::ggcompoplot(bebug_dapc, setPop(bebug, ~Region), cols = 5, pal = viridis::plasma(3, end = 0.85)) +
  theme(legend.position = "top")
```

```{r dapc_hr, fig.width = 5, fig.height = 5.5}
setPop(bebug) <- ~Host/Region
bebug_dapc <- dapc(bebug, n.pca = 20, n.da = 20)
bebug_dapc
```

```{r ggdapc, fig.width = 8, fig.height = 4}
LDS <- bind_cols(Population = bebug_dapc$grp, as.data.frame(bebug_dapc$ind.coord)) %>%
  as_tibble()
LDS_pop <- LDS %>% 
  group_by(Population) %>% 
  summarize_all(mean) %>%
  rename_all(function(x) gsub("LD", "mean", x))
LDS <- full_join(LDS, LDS_pop, by = "Population") %>% separate(Population, c("Cultivar", "Population"))
LDS_PLOT <- ggplot(LDS, aes(x = LD1, y = LD2, color = Cultivar)) + 
  geom_point(aes(fill = Cultivar), alpha = 0.5, pch = 21, color = "black") +
  geom_segment(aes(x = mean1, y = mean2, xend = LD1, yend = LD2), alpha = 0.5) +
  stat_ellipse(type = "norm", level = 0.66, alpha = 0.75) + 
  theme_bw(base_size = 16, base_family = "Helvetica") +  
  theme(aspect.ratio = 1/1.618) +
  theme(legend.position = "bottom") +
  theme(axis.text = element_blank()) + 
  theme(axis.title = element_blank()) + 
  theme(axis.ticks = element_blank()) + 
  viridis::scale_color_viridis(option = "B", discrete = TRUE, direction = -1, end = 0.85) +
  viridis::scale_fill_viridis(option = "B", discrete = TRUE, direction = -1, end = 0.85) +
  scale_y_continuous(breaks = 0) + 
  scale_x_continuous(breaks = 0) + 
  theme(panel.background = element_rect(fill = "grey95")) +
  theme(panel.grid.major = element_line(color = "black")) +
  facet_wrap(~Population, nrow = 2)
LDS_PLOT
```
